paper1_results_figs_slimmed_50_rr

### 2016-06-24 inst/documents/paper1_results_figs_rr.Rmd
adding checks of number runs not reaching resistance thresholds, changing figs to effectiveness_added and dominance_added

  #create a curtisInputs dataframe for use later
  curtisInputs <- data.frame("exposure"=0.9,
                             "effectiveness_insecticide1"=0.73,
                             "effectiveness_insecticide2"=1,
                             "start_freq_allele1"=0.01,
                             "start_freq_allele2"=0.01,
                             "dominance_allele1"=0.17,
                             "dominance_allele2"=0.0016,
                             # 14/6/16 rr_advantage = s / effectiveness
                             #"selection_coef_allele1"=0.23,
                             #"selection_coef_allele2"=0.43,
                             "rr_advantage_I1"=0.23/0.73,
                             "rr_advantage_I2"=0.43/1,                             
                             "maleExposureProp"=1,
                             "correctMixDeployProp"=1,
                             "resist_start_lo_div_hi"=1,
                             "resist_start_1_div_2"=1)

@@

```{r, eval=TRUE, echo=FALSE, warning=FALSE} 
# getting data into format for ggplot

@@

@@

```{r, eval=FALSE, echo=FALSE, fig.height=3.5}

  #10/5/2016 seems to crash R, so set to eval=FALSE

@@

    y <- 'time_to_resistance0.5'

    #print( ggplot(ggInsOuts, aes_string(x=i, y=y, colour="strategy")) + 
    print( ggplot(ggSubset, aes_string(x=i, y=y, colour="strategy")) + 
            #points not wanted if 10000
             #geom_point(shape=3, show.legend=FALSE) + 
             #geom_smooth(colour='red', linetype='dashed',size=0.5) +
             geom_smooth(linetype='dashed',size=1) +
             #facet_wrap( ~ strategy) +
             #geom_smooth(aes_string(x=i, y=y, color=NULL)) )
             labs(title = i) +
             #add line for Curtis inputs
             geom_vline(data = curtisInputs, aes_string(xintercept = i), linetype='dotted', colour='red') +
             #tryting to get the vline into the legend fails
             #geom_vline(data = curtisInputs, aes_string(xintercept = i, colour='"Curtis Fig.2"' ), linetype='dotted', show.legend=TRUE) +
             geom_text(data = curtisInputs, inherit.aes = FALSE, aes_string(x = i, y=210, label='"Curtis Fig.2"'), size=3, colour='red')

           )
  }

>>>>

  #create a curtisInputs dataframe for use later
  curtisInputs <- data.frame("exposure"=0.9,
                             "effectiveness_insecticide1"=0.73,
                             "effectiveness_insecticide2"=1,
                             "effectiveness_added"=1.73,                             
                             "start_freq_allele1"=0.01,
                             "start_freq_allele2"=0.01,
                             "dominance_allele1"=0.17,
                             "dominance_allele2"=0.0016,
                             "dominance_added"=0.1716,                             
                             # 14/6/16 rr_advantage = s / effectiveness
                             #"selection_coef_allele1"=0.23,
                             #"selection_coef_allele2"=0.43,
                             "rr_advantage_I1"=0.23/0.73,
                             "rr_advantage_I2"=0.43/1,                             
                             "maleExposureProp"=1,
                             "correctMixDeployProp"=1,
                             "resist_start_lo_div_hi"=1,
                             "resist_start_1_div_2"=1)

@@

```{r, eval=TRUE, echo=FALSE, warning=FALSE} 
# getting data into format for ggplot
  library(ggplot2)

@@

  # #23/6/2016 add a check for which runs are being excluded (note that some are excluded in a different place too) 
  # #just those runs that didn't make threshold
  ggSubset <- ggInsOuts[didntReachThresh,]
  names_inputs <- names(ggInsOuts)[1:num_inputs]
  # 
  # ggSubset <- ggSubset[ !ggSubset$strategy %in% c("insecticide 1","insecticide 2"), ]
  # 
  # for(i in names_inputs)
  # {
  #   y <- 'time_to_resistance0.5'    
  #   
  #   print( ggplot(ggSubset, aes_string(x=i, y=y, colour="strategy")) + 
  #            
  #            geom_point(shape=3) #, show.legend=FALSE) + 
  #            #geom_smooth(linetype='dashed',size=1)
  #          )
  # }

  # #seems that most failed runs are at low start freqs
  # hist(ggSubset$start_freq_allele1)
  # #compare to all runs
  # hist(ggInsOuts$start_freq_allele1)  
  # #and for start freqs combined
  # hist(ggSubset$start_freq_allele1+ggSubset$start_freq_allele2)
  # #compare to all runs
  # hist(ggInsOuts$start_freq_allele1+ggInsOuts$start_freq_allele2)
  # #also low exposure is a large contributor to failed runs
  # hist(ggSubset$exposure)  
  # #compared to all runs
  # hist(ggInsOuts$exposure)

  #quick look at low start freq runs. Can they make it to thresholds ? Yes
  # for(i in names_inputs)
  # {
  #   y <- 'time_to_resistance0.5'    
  #   
  #   print( ggplot(ggInsOuts[ggInsOuts$start_freq_allele1 < 0.001 & ggInsOuts$start_freq_allele2 < 0.001,], aes_string(x=i, y=y, colour="strategy")) + 
  #            
  #            geom_point(shape=3) + #, show.legend=FALSE) + 
  #            geom_smooth(linetype='dashed',size=1)
  #          )
  # }

  ####### end of new check

@@

@@

  ggSubset$effectiveness_added <- ggSubset$effectiveness_insecticide1 + ggSubset$effectiveness_insecticide2
  ggSubset$dominance_added <- ggSubset$dominance_allele1 + ggSubset$dominance_allele2
  names_inputs <- c(names_inputs, "effectiveness_added", "dominance_added")

  for(i in names_inputs)
  {
    y <- 'time_to_resistance0.5'

    print( ggplot(ggSubset, aes_string(x=i, y=y, colour="strategy")) +

             geom_point(shape=3, size=0.2, alpha=0.2, show.legend=FALSE) + 
             geom_smooth(linetype='dashed',size=1) +

             #labs(title = i) +
             #add line for Curtis inputs
             geom_vline(data = curtisInputs, aes_string(xintercept = i), linetype='dotted', colour='red') +
             geom_text(data = curtisInputs, inherit.aes = FALSE, aes_string(x = i, y=210, label='"Curtis Fig.2"'), size=3, colour='red')
           )
  }

## Fig. xx2 Quick check whether difference between effectiveness 1 & 2 dissapears when minimising excluded runs

  #names_inputs <- names(ggInsOuts)[1:num_inputs]
  names_inputs <- c("effectiveness_insecticide1", "effectiveness_insecticide2", "effectiveness_added")

  ggSubset <- ggInsOuts[ !ggInsOuts$strategy %in% c("insecticide 1","insecticide 2","Mix either","Sequential"), ]

  ggSubset$effectiveness_added <- ggSubset$effectiveness_insecticide1 + ggSubset$effectiveness_insecticide2

  # ggSubset <- ggSubset[ ggSubset$start_freq_allele1 > 0.005 & 
  #                       ggSubset$start_freq_allele2 > 0.005 &
  #                       ggSubset$dominance_allele1 > 0.1 &
  #                       ggSubset$dominance_allele2 > 0.1 &
  #                       ggSubset$exposure > 0.3  , ]

  for(i in names_inputs)
  {
    y <- 'time_to_resistance0.5'

    print( ggplot(ggSubset, aes_string(x=i, y=y, colour="strategy")) +

             geom_point(shape=1, size=1, alpha=0.2, show.legend=FALSE) + 
             geom_smooth(linetype='dashed',size=1)

             #labs(title = i) +
             #add line for Curtis inputs
             #geom_vline(data = curtisInputs, aes_string(xintercept = i), linetype='dotted', colour='red') +
             #geom_text(data = curtisInputs, inherit.aes = FALSE, aes_string(x = i, y=210, label='"Curtis Fig.2"'), size=3, colour='red')
           )
  }

### 2016-06-24 inst/documents/paper1_results_figs_slimmed_50_rr.Rmd
adding checks of number runs not reaching resistance thresholds, changing figs to effectiveness_added and dominance_added

@@

  #remove runs that didn't reach a resistance threshold (999), even if just for one strategy
  #>1000 excludes sequential strategy that had a 999 in
  #BEWARE would need to increase 1000 if I increase max generations in the runs
  didntReachThresh <- which( dif_mixA_seq$gen_cP0.5 > 500 | dif_mixA_seq$gen_cP0.5seq > 500 )
  #subset by runs not making threshold
  dif_mixA_seq <- dif_mixA_seq[-didntReachThresh,]

@@

  #for dif_mix2_seq
  didntReachThresh <- which( dif_mix2_seq$gen_cP0.5 > 500 | dif_mix2_seq$gen_cP0.5seq > 500 )
  #subset by runs not making threshold
  dif_mix2_seq <- dif_mix2_seq[-didntReachThresh,]

@@

  print( ggplot(ggSubset, aes_string(x='strategy',y=i, color='strategy')) + 
      #ylim(0,450) +
      coord_cartesian( ylim=c(0, 350)) +
      geom_violin(draw_quantiles = c(0.25, 0.75), show.legend=FALSE, adjust = .5 ) +
      ylab('Time to resistance (gens)') +
      scale_x_discrete("", limits=c("insecticide 1","Mix either","Sequential","Mix adaptive","Mix both"), labels = c("insecticide 1"="Seq 1st", "Mix either"="Mix 1st","Sequential"="Seq both", "Mix adaptive"="Adaptive", "Mix both"="Mix both" ) )

@@

  #in main paper I want to just display sequential and mixture strategies
  strategies <- c("Sequential", "Mix adaptive", "Mix both")
  strat_name <- c("Seq both","Adaptive both","Mix both")

@@

  #names_inputs <- names(ggInsOuts)[1:num_inputs]

  #remove insecticide1 & 2 strategies
  #ggSubset <- ggInsOuts[ !ggInsOuts$strategy %in% c("insecticide 1","insecticide 2"), ]
  #20/6/16 try also removing "Mix either" 
  ggSubset <- ggInsOuts[ !ggInsOuts$strategy %in% c("insecticide 1","insecticide 2","Mix either"), ]

  #subset which output plots to show in the main paper
  # in_cols <- c("start_freq_allele1", "exposure","effectiveness_insecticide1",
  #             "dominance_allele1","selection_coef_allele1","maleExposureProp")
  in_cols <- c("exposure","effectiveness_insecticide1","dominance_allele1")

@@

  #num_inputs <- length(in_cols)
  #names_inputs <- in_cols

  #to rearrange order of legend entries
  #ggSubset$strategy <- factor(ggSubset$strategy, levels=c("Mix both", "Mix adaptive", "Sequential", "Mix either")) 
  #20/6/16 try removing "Mix either" 
  ggSubset$strategy <- factor(ggSubset$strategy, levels=c("Mix both", "Mix adaptive", "Sequential"))

  #TODO could I facet the plots below rather than using the loop
  #probably need to put all inputs into a single column and then facet by that

  #for(i in names_inputs)
  for(i in in_cols)
    {
    #x11()

@@

    #print( ggplot(ggInsOuts, aes_string(x=i, y=y, colour="strategy")) + 
    print( ggplot(ggSubset, aes_string(x=i, y=y, colour="strategy")) + 
            #points not wanted if 10000
             #geom_point(shape=3, show.legend=FALSE) + 
             #geom_smooth(colour='red', linetype='dashed',size=0.5) +
             geom_smooth(linetype='dashed',size=0.5) +
             #facet_wrap( ~ strategy) +
             #geom_smooth(aes_string(x=i, y=y, color=NULL)) )
             #labs(title = i) +
             #add line for Curtis inputs
             geom_vline(data = curtisInputs, aes_string(xintercept = i), linetype='dotted', colour='red') +
             #tryting to get the vline into the legend fails
             #geom_vline(data = curtisInputs, aes_string(xintercept = i, colour='"Curtis Fig.2"' ), linetype='dotted', show.legend=TRUE) +
             geom_text(data = curtisInputs, inherit.aes = FALSE, aes_string(x = i, y=210, label='"Curtis Fig.2"'), size=3, colour='red')

@@

1. Exposure and effectiveness come out as the most important effect on the difference between the sequential and adpative mixture strategies.

@@

@@

>>>>

  #22/6/2016 to check % of runs excluded 
  #its complicated given that there are runs for I1,I2 & mix 
  #this is an approximation
  #TODO, are any others excluded later ?
  percentExcluded <- 100*length(didntReachThresh)/nrow(ggInsOuts)
  #16.5

@@

  #remove runs that didn't reach a resistance threshold (999), even if just for one strategy
  #>1000 excludes sequential strategy that had a 999 in
  #BEWARE would need to increase 1000 if I increase max generations in the runs
  didntReachThresh <- which( dif_mixA_seq$gen_cP0.5 > 500 | dif_mixA_seq$gen_cP0.5seq > 500 )

  #TODO 22/6/16 RECHECK that nothing dodgy going on here, seems that more runs being excluded
  #but this is because its going back to the raw files
  percentExcluded2 <- 100*length(didntReachThresh)/nrow(dif_mixA_seq)
  #24%

  #subset by runs not making threshold
  dif_mixA_seq <- dif_mixA_seq[-didntReachThresh,]

@@

  #for dif_mix2_seq
  didntReachThresh <- which( dif_mix2_seq$gen_cP0.5 > 500 | dif_mix2_seq$gen_cP0.5seq > 500 )

  percentExcluded3 <- 100*length(didntReachThresh)/nrow(dif_mix2_seq)
  #30%

  ####################
  #23/6/2016 experimenting to see if can reduce the % excluded by tweaking input ranges
  #20%
  #dif_mix2_seq2 <- dif_mix2_seq[ dif_mix2_seq$start_freq_allele1 > 0.005, ]
  #16%
  #dif_mix2_seq2 <- dif_mix2_seq[ dif_mix2_seq$start_freq_allele1 > 0.005 & dif_mix2_seq$start_freq_allele2 > 0.005, ]
  #18%
  #dif_mix2_seq2 <- dif_mix2_seq[ dif_mix2_seq$exposure > 0.25, ]
  #16%
  #dif_mix2_seq2 <- dif_mix2_seq[ dif_mix2_seq$exposure > 0.3, ]
  #7%
  #dif_mix2_seq2 <- dif_mix2_seq[ dif_mix2_seq$start_freq_allele1 > 0.005 & dif_mix2_seq$start_freq_allele2 > 0.005 & dif_mix2_seq$exposure > 0.25, ]   
  #5%
  #dif_mix2_seq2 <- dif_mix2_seq[ dif_mix2_seq$start_freq_allele1 > 0.005 & dif_mix2_seq$start_freq_allele2 > 0.005 & dif_mix2_seq$exposure > 0.3, ] 
  #26%
  #dif_mix2_seq2 <- dif_mix2_seq[ dif_mix2_seq$effectiveness_insecticide1 > 0.4 & dif_mix2_seq$effectiveness_insecticide2 > 0.4, ]
  #13%
  #dif_mix2_seq2 <- dif_mix2_seq[ dif_mix2_seq$effectiveness_insecticide1 > 0.4 & dif_mix2_seq$effectiveness_insecticide2 > 0.4 & dif_mix2_seq$exposure > 0.3, ]
  #10%
  #dif_mix2_seq2 <- dif_mix2_seq[ dif_mix2_seq$start_freq_allele1 > 0.001 & dif_mix2_seq$start_freq_allele2 > 0.001 & dif_mix2_seq$exposure > 0.3, ] 
  #8%
  #dif_mix2_seq2 <- dif_mix2_seq[ dif_mix2_seq$effectiveness_insecticide1 > 0.4 & dif_mix2_seq$effectiveness_insecticide2 > 0.4 & dif_mix2_seq$start_freq_allele1 > 0.001 & dif_mix2_seq$start_freq_allele2 > 0.001 & dif_mix2_seq$exposure > 0.3, ] 
  #22%
  #dif_mix2_seq2 <- dif_mix2_seq[ dif_mix2_seq$dominance_allele1 > 0.1 & dif_mix2_seq$dominance_allele2 > 0.1, ] 
  #5%
  #dif_mix2_seq2 <- dif_mix2_seq[ dif_mix2_seq$start_freq_allele1 > 0.001 & dif_mix2_seq$start_freq_allele2 > 0.001 & dif_mix2_seq$exposure > 0.3 & dif_mix2_seq$dominance_allele1 > 0.1 & dif_mix2_seq$dominance_allele2 > 0.1, ]

  # didntReachThresh <- which( dif_mix2_seq2$gen_cP0.5 > 500 | dif_mix2_seq2$gen_cP0.5seq > 500 )
  # 
  # percentExcluded4 <- 100*length(didntReachThresh)/nrow(dif_mix2_seq2)
  # 
  # percentExcluded4

  #### end of expt 23/6/2016

  #subset by runs not making threshold
  dif_mix2_seq <- dif_mix2_seq[-didntReachThresh,]

@@

  print( ggplot(ggSubset, aes_string(x='strategy',y=i, color='strategy')) + 
      #ylim(0,450) +
      coord_cartesian( ylim=c(0, 350)) +
      geom_violin(draw_quantiles = c(0.25, 0.75), show.legend=FALSE, adjust = .5 ) +
      ylab('Time to resistance (gens)') +
      scale_x_discrete("", limits=c("insecticide 1","Mix either","Sequential","Mix adaptive","Mix both"), labels = c("insecticide 1"="Seq 1st", "Mix either"="Mix 1st","Sequential"="Seq both", "Mix adaptive"="Adaptive both", "Mix both"="Mix both" ) )

@@

  #in main paper I want to just display sequential and mixture strategies
  strategies <- c("Sequential", "Mix adaptive", "Mix both")
  strat_name <- c("Sequential both","Adaptive both","Mix both")

@@

  #remove some strategies for plots
  ggSubset <- ggInsOuts[ !ggInsOuts$strategy %in% c("insecticide 1","insecticide 2","Mix either"), ]

  # create added columns for effectiveness and dominance
  ggSubset$effectiveness_added <- ggSubset$effectiveness_insecticide1 + ggSubset$effectiveness_insecticide2
  ggSubset$dominance_added <- ggSubset$dominance_allele1 + ggSubset$dominance_allele2

  #subset which output plots to show in the main paper
  # in_cols <- c("start_freq_allele1", "exposure","effectiveness_insecticide1",
  #             "dominance_allele1","selection_coef_allele1","maleExposureProp")
  #in_cols <- c("exposure","effectiveness_insecticide1","dominance_allele1")  
  in_cols <- c("exposure","effectiveness_added","dominance_added")

@@

  #to rearrange order of legend entries
  ggSubset$strategy <- factor(ggSubset$strategy, levels=c("Mix both", "Mix adaptive", "Sequential", "Mix either")) 
  #20/6/16 try removing "Mix either" 
  #ggSubset$strategy <- factor(ggSubset$strategy, levels=c("Mix both", "Mix adaptive", "Sequential"))

  #for(i in names_inputs)
  for(i in in_cols)
    {

@@

    #print( ggplot(ggInsOuts, aes_string(x=i, y=y, colour="strategy")) + 
    print( ggplot(ggSubset, aes_string(x=i, y=y, colour="strategy")) +

             #ideally would include points but they obscure means
             #geom_point(shape=1, size=1, alpha=0.2, show.legend=FALSE) + 
             geom_smooth(linetype='dashed',size=0.5) +
             #facet_wrap( ~ strategy) +
             #labs(title = i) +
             #add line for Curtis inputs
             geom_vline(data = curtisInputs, aes_string(xintercept = i), linetype='dotted', colour='red') +
             #trying to get the vline into the legend fails
             #geom_vline(data = curtisInputs, aes_string(xintercept = i, colour='"Curtis Fig.2"' ), linetype='dotted', show.legend=TRUE) +
             geom_text(data = curtisInputs, inherit.aes = FALSE, aes_string(x = i, y=210, label='"Curtis Fig.2"'), size=3, colour='red')

@@

1. Exposure and effectiveness come out as the most important effect on the difference between A) sequential and mixture, and B) difference between sequential and adaptive mixture strategies.

@@

    cat("A)")

@@

    cat("B)")
